Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-29 draft/paper1_jenny.tex
Edit Mtotal

    We construct five band SEDs using the forced-photometry \cmodel{} magnitudes 
    corrected for Galactic extinction. 
    \cmodel{} only accounts for the statistical error on the flux measurement but 
    does not account for systematic uncertainties in the model-fitting process. 
    It therefore underestimates the flux errors of bright galaxies. 
    For this work, we supply \texttt{iSEDFit} with simplified flux errors assuming 
    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$ and $y$ band 
    (on average, images in $gy$ bands are shallower in depth and/or have higher 
    background noise).  
    Although these are still conservative estimates of the systematic uncertainties 
    involved in the model-fitting, tests using synthetic galaxies show that \cmodel{}
    provides excellent measurements of five-band colors, which are crucial for 
    reliable \m2l{} estimates.
    The typical uncertainty of \logms{} is around 0.06-0.08 dex at \logms${\sim} 11.5$. 
    Please see Appendix~\ref{app:sed} for further details.

@@

    Using the best-fit stellar mass from \texttt{iSEDFit} (noted as as \mcmodel{}), 
    we estimate the average \m2l{} in the $i$-band, then use that \m2l{} to convert 
    our 1-D luminosity density profiles into stellar mass density (\mden{}) profiles. 
    We also convert our 10 and 100 kpc aperture luminosities into corresponding stellar 
    mass estimates (noted as \minn{} and \mtot{}).

    For the remainder of this paper, we will use \mtot{} as a proxy of ``total'' 
    stellar mass. 
    \update{
    As expected, the integration of the 1-D profile out to very large radius recovers 
    more luminosity (stellar mass) compared to the \cmodel{}-based estimates 
    (Fig \ref{fig:mass_diff}).
    }
    \song{Work in progress.}

    In Appendix~\ref{app:sed}, we briefly summarize the basic statistics of 
    the sample using our estimates of \mtot{} and \minn{}.
    We confirm that the sample follows a very tight ``red-sequence'' that does not appear to depend on 
    environment (see \S XX). 
    Appendix~\ref{app:sed} describes the outputs from our SED fitting process 
    (average stellar age, metallicity, and internal dust extinction). 
    We do not utilize these quantities in this paper, but we have checked that they all 
    behave reasonably for both samples.

    \song{The color gradients and ellipticity profiles will be updated}
    Our methodology ignores any radial variations in \m2l{}. 
    It is well known that massive ETGs have negative optical color gradients indicating 
    gradients in \m2l{} (e.g.\ \citealt{LaBarbera2012}; 
    \citealt{DSouza2015}). \jenny{earlier reference here?}
    These color gradients are shallow and smooth out to a few times the effective 
    radius and color gradients at the outskirts are not yet well quantified.
    Our results looking at the outer envelopes as a function of mass and environment 
    will be robust as long as there is \emph{no significant difference in 
    the average color gradient between sub-samples}.
    %More importantly, for the comparison between the \rbcg{} and \nbcg{} samples, 
    %our results will be robust as long as there is \emph{no significant difference in 
    %the average color gradient between the two samples}. 
    We have confirmed that this is indeed the case (see Section~\ref{ssec:ell_color}).

>>>>

    We construct five band SEDs using the forced-photometry \cmodel{} magnitudes 
    corrected for Galactic extinction. 
    \cmodel{} only accounts for the statistical error on the flux measurement but 
    does not account for systematic uncertainties in the model-fitting process. 
    It therefore underestimates the flux errors of bright galaxies. 
    For this work, we supply \texttt{iSEDFit} with simplified flux errors assuming 
    $S/N = 100$ for the $riz$ bands, and $S/N = 80$ for the $g$ and $y$ band 
    (on average, images in $gy$ bands are shallower in depth and/or have higher 
    background noise).  
    Although these are still conservative estimates of the systematic uncertainties 
    involved in the model-fitting, tests using synthetic galaxies show that \cmodel{}
    provides excellent measurements of five-band colors, which are crucial for 
    reliable \m2l{} estimates.
    The typical uncertainty of \logms{} is around 0.06-0.08 dex at \logms${\sim} 11.5$.

    In Appendix~\ref{app:sed}, we briefly summarize the basic statistics of 
    the sample, including average stellar age, metallicity, and internal dust 
    extinction along with their relation with \mtot{}. 
    All these properties behave reasonably for massive galaxies in this sample despite 
    that we do not utilize them in this paper. 
    Using the $k$-corrected optical color, we can also confirm that the sample follows 
    a tight ``red-sequence''.  
    Please see Appendix~\ref{app:sed} for further details.

@@

    Using the best-fit \mstar{} from \texttt{iSEDFit} (noted as as \mcmodel{}), 
    we estimate the average \m2l{} in the $i$-band, then use that \m2l{} to convert 
    our 1-D luminosity density profiles into stellar mass density (\mden{}) profiles. 
    We also convert our 10 and 100 kpc aperture luminosities into corresponding stellar 
    mass estimates (noted as \minn{} and \mtot{}).

    For the remainder of this paper, we will use \mtot{} as a proxy of ``total'' 
    stellar mass. 
    As expected, the integration of the 1-D profile out to very large radius recovers 
    more luminosity (stellar mass) compared to the \cmodel{}-based estimates 
    (Fig \ref{fig:mass_diff}).
    At high-\mstar{} end (e.g. \logmtot{}$>11.6$), the average difference is larger 
    than 0.1 dex and can be as large as 0.2--0.3 dex.  
    More importantly, the differences between \mtot{} and \mcmodel{} clearly show 
    dependence on total stellar mass as \mcmodel{} tends to misse more light in 
    more massive galaxies.  
    In the next section, we will show that this

    Our methodology ignores any radial variations in \m2l{}. 
    It is well known that massive ETGs have negative optical color gradients 
    indicating gradients in \m2l{} (e.g.\ \citealt{LaBarbera2012}; 
    \citealt{DSouza2015}). \jenny{earlier reference here?}
    These color gradients are shallow and smooth out to a few times the effective 
    radius and color gradients at the outskirts are not yet well quantified.
    Our results looking at the outer envelopes as a function of mass and environment 
    will be robust as long as there is \emph{no significant difference in 
    the average color gradient between sub-samples}.
    %More importantly, for the comparison between the \rbcg{} and \nbcg{} samples, 
    %our results will be robust as long as there is \emph{no significant difference in 
    %the average color gradient between the two samples}. 
    We have confirmed that this is indeed the case (see Section~\ref{ssec:ell_color}).
